---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


##Loading and proccesing the data



```{r}
data<-read.csv("activity.csv")
```


##What is mean total number of steps taken per day?
###1:Histogram of the total number of steps taken each day

```{r Histogram}
library(ggplot2)
steps.date<-aggregate(steps~date, data=data, FUN = sum)
p<-qplot(steps.date$steps, geom="histogram")
p
```

###2: Mean and median total number of steps taken per day

```{r Mean, results=FALSE}
mean.steps<-mean(steps.date$steps)
median.steps<-median(steps.date$steps)
```

The mean: `r mean.steps`  
The median: `r median.steps`


##What is the average daily activity pattern?

1. A plot of the average steps per interval:

```{r}
steps.interval<-aggregate(steps~interval, data=data, FUN = mean)
plot(y=steps.interval$steps, x=steps.interval$interval, type = "l",  
     ylab = "Mean steps per interval", xlab = "Interval")

```

2. Calculate the interval with the highest average steps:

```{r Max.steps}
max.steps<-steps.interval[which.max(steps.interval$steps),1]

```

The interval with the highest average steps is `r max.steps`

##Imputing missing values

1. The number of NA rows:

```{r NA}
num.na<-sum(is.na(data$steps))
```

The number of rows without data is: `r num.na`

2. I will fill the missing data with the average steps per interval:

```{r fill.na}
data.fill<-data
for (i in 1 : nrow(data.fill)) {  
  if(is.na(data.fill[i,]$steps)) {  
   data.fill[i,]$steps<-steps.interval[steps.interval$interval==data.fill[i,]$interval,]$steps
          }
  }
```

3. The new dataset is named: "data.fill"

4.
4.1:Histogram

```{r new.histogram}

steps.date.new<-aggregate(steps~date, data=data.fill, FUN = sum)
p<-hist(steps.date.new$steps, geom="histogram")
```

4.2: mean and median:

```{r Mean.new, results=FALSE}
mean.steps.new<-mean(steps.date.new$steps)
median.steps.new<-median(steps.date.new$steps)
```
 The new mean is `r mean.steps.new`
 The new median is `r median.steps.new`
 
 Their is no big difference in the mean an in the median, yet there is a diffrence in the histogram, the results make sence becaouse of the way the mean and median is calculate. 
 
## Differences in activity patterns between weekdays and weekends

1: Adding to the date if the activity where in weekdays or in weekend:

```{r weekdays}
weekdays<-weekdays(as.Date((data.fill$date)))
sabat<-weekdays=="שבת"
sunday<-weekdays==names(table(weekdays))[2]
weekend_day<-sabat+sunday
weekend<-vector(length = nrow(data.fill))
weekend[weekend_day==1]<-"Weekend"
weekend[weekend_day==0]<-"Weekday"
data.fill$weekend<-weekend
```
 
 
2: A plot by Weekend/Weekday

```{r weekdays plot}
steps.day <- aggregate(steps ~ interval + weekend, data = data.fill, mean)
library("lattice")
xyplot(steps ~ interval | weekend, steps.day, type = "l", layout = c(1, 2), 
    xlab = "Interval", ylab = "Number of steps")
```